|

### 2023-02-03 paper.Rmd
autogit
Fri Feb  3 12:00:08 CET 2023: update-remote.sh

@@

One major drawback of using pre-training with DAE-GP

@@

<!-- * der Erhöhung der Populationsdiversität (mögliche Strategie zur Kontrolle des Explore/Exploit Verhaltens von DAE-GP?) -->

@@

<!-- * DAE-GP verliert durch Einsatz von Pre-Training die Möglichkeit die Anzahl künstlicher Neuronen pro verstecktem Layer anzupassen -->

>>>>

### EDA-GP

... insert some smart stuff here...

@@

As detailed in the subsection [Dynamic Adjustment of Hidden Neurons], one major drawback of using pre-training with DAE-GP is the loss of the ability to dynamically adjust the number of hidden neurons to the maximum size of individuals inside the current generations population. This dynamic mechanism does reduce the computational resources necessary for training DAE-LSTM networks which is one of the most time consuming operations besides sampling new individuals.

Another disadvantage of pre-training in DAE-GP is that in order for it to show

@@

@@

### 2023-02-03 paper.tex
Fri Feb  3 12:00:08 CET 2023: update-remote.sh

@@

One major drawback of using pre-training with DAE-GP

>>>>

\hypertarget{eda-gp}{%
\subsubsection{EDA-GP}\label{eda-gp}}

\ldots{} insert some smart stuff here\ldots{}

@@

As detailed in the subsection {[}\protect\hyperlink{ref-Dynamic}{\textbf{Dynamic?}} Adjustment of Hidden Neurons{]}, one major drawback of using pre-training with DAE-GP is the loss of the ability to dynamically adjust the number of hidden neurons to the maximum size of individuals inside the current generations population. This dynamic mechanism does reduce the computational resources necessary for training DAE-LSTM networks which is one of the most time consuming operations besides sampling new individuals.

Another disadvantage
